Large and Infinitary Quotient Inductive-Inductive Types

### 2020-05-03 draft/paper.tex
fix

\begin{definition}[Signature for ToS] For each level $j$,
we define $\ToSSig_j : \Sig_{j+i}$, as the signature for the theory of
signatures with external sets in $\Set_j$. This is a large and infinitary QIIT
signature, as we have $\Pie$ and $\Piinf$ abstracting over $A : \Set_j$ and
branching with $A \ra \Ty\,\Gamma$ and $A \ra \Tm\,\Gamma\,\U$ respectively. We
present an excerpt from $\ToSSig_j$ below.
\begin{alignat*}{3}
  & \emptycon && \ext (Con : \U)\\
  &           && \ext (Sub : Con\arri Con \arri \U)\\
  &           && \ext (Ty  : Con\arri\U)\\
  &           && \ext (Tm  : \Pii(\Gamma : Con)(\Ty\,\Gamma \arri \U))\\
  &           && ...\\
  &           && \ext (\Piinf : \Pii(\Gamma : Con)\\
  &           && \hspace{4.2em}(\Pie \Set_j (\lambda\,A.\,(A \arrinf \Ty\,\Gamma)\arri\El(\Ty\,\Gamma))))\\
  &           && ...
\end{alignat*}
\end{definition}

>>>>

\begin{definition}[Signature for ToS] For each level $j$,
we define $\ToSSig_j : \Sig_{j+i}$, as the signature for the theory of
signatures with external sets in $\Set_j$. This is a large and infinitary QIIT
signature, as we have $\Pie$ and $\Piinf$ abstracting over $A : \Set_j$ and
branching with $A \ra \Ty\,\Gamma$ and $A \ra \Tm\,\Gamma\,\U$ respectively. We
present an excerpt from $\ToSSig_j$ below.
\begin{alignat*}{3}
  & \emptycon && \ext (Con : \U)\\
  &           && \ext (Sub : Con\arri Con \arri \U)\\
  &           && \ext (Ty  : Con\arri\U)\\
  &           && \ext (Tm  : \Pii(\Gamma : Con)(\Ty\appitt\Gamma \arri \U))\\
  &           && ...\\
  &           && \ext (\Piinf : \Pii(\Gamma : Con)\\
  &           && \hspace{4.2em}(\Pie \Set_j (\lambda\,A.\,(A \arrinf \Ty\appitt\Gamma)\arri\El(\Ty\appitt\Gamma))))\\
  &           && ...
\end{alignat*}
\end{definition}
